---
title: "style model"
output:
  md_document:
    variant: markdown_github
  html_document:
   toc: true
   theme: united
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("styleTest.csv")
data$count <- (data$id %% 10) * 200
data$type <- data$id %/% 10
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout

data$typeName <- ifelse(data$type == 0, ".a .c", ifelse(data$type == 1, ".b ~ .c", ".c"))
means$typeName <- ifelse(means$type == 0, ".a .c", ifelse(means$type == 1, ".b ~ .c", ".c"))

library(ggplot2)
library(nnls)

```

Comparison of single selectors ".a .c", ".b ~ .c", and ".c" matching against variable number of element subtrees:

```
<div class='a'>
  <div class='b'>
  </div>
  <div class='c'>
  </div>
</div>
```

Three properties are set in a single rule:

```
%SEL {
  background-color: red;
  width: 100px;
  height: 100px;
}
```

Graphs contain `r length(data$id)` samples.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser, group=type, colour=typeName)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout, group=type, colour=typeName)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("styleTest2.csv")
data$count <- (data$id %% 10) * 200
data$type <- data$id %/% 10
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout

data$typeName <- ifelse(data$type == 0, ".a .c", ifelse(data$type == 1, ".b ~ .c", ".c"))
means$typeName <- ifelse(means$type == 0, ".a .c", ifelse(means$type == 1, ".b ~ .c", ".c"))
```

As above, but without whitespace between divs (to avoid O(N^2) style). Graphs contain `r length(data$id)` samples.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser, group=type, colour=typeName)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout, group=type, colour=typeName)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("whitespace.csv")
data$count <- (data$id %/% 10) * 200
data$type <- data$id %% 10
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout

data$typeName <- ifelse(data$type == 0, "no whitespace", "whitespace")
means$typeName <- ifelse(means$type == 0, "no whitespace", "whitespace")
```

Looking at just whitespace. Graphs contain `r length(data$id)` samples.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser, group=type, colour=typeName)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout, group=type, colour=typeName)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
nws <- means[means$type == 0,]
basefit <- lm(nws$Document..updateStyle ~ poly(nws$count, 1, raw=TRUE))

ws <- means[means$type == 1,]
ws$Document..updateStyle = ws$Document..updateStyle - basefit$coefficients[1] - ws$count * basefit$coefficients[2];
A <- matrix(c(ws$count, ws$count^2), nrow=length(ws$count))
fit <- nnls::nnls(A, ws$Document..updateStyle)
ws$Document..updateStyle = ws$Document..updateStyle + basefit$coefficients[1] + ws$count * basefit$coefficients[2];

```

Without text nodes, the cost of updateStyle is linear, with an intercept of `r basefit$coefficients[1]` and a slope of `r basefit$coefficients[2]`.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(nws, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line() + geom_abline(intercept=basefit$coefficients[1], slope=basefit$coefficients[2])
```

Introducing whitespace gives a cost that we assume fits a quadratic with 0 intercept, and constrained positive parameters of `r fit$x`.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ws$sample <- basefit$coefficients[1] + ws$count * (fit$x[1] + basefit$coefficients[2]) + ws$count^2 * fit$x[2]
ggplot(ws, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line() + geom_line(aes(y=sample), colour="black")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("nostyle.csv")
data$count <- (data$id %/% 10) * 200
data$type <- data$id %% 10
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout

data$typeName <- ifelse(data$type == 0, "no whitespace", "whitespace")
means$typeName <- ifelse(means$type == 0, "no whitespace", "whitespace")
```

No style at all (with and without whitespace). Graphs contain `r length(data$id)` samples.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser, group=type, colour=typeName)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout, group=type, colour=typeName)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("styleTest3.csv")
data$count <- (data$id %/% 10) * 200
data$type <- data$id %% 10
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout

data$typeName <- ifelse(data$type == 0, "sibling", "child")
means$typeName <- ifelse(means$type == 0, "sibling", "child")
```

styleTest3

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser, group=type, colour=typeName)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout, group=type, colour=typeName)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("styleTest4.csv")
data$count <- (data$id %% 10) * 200
data$type <- data$id %/% 10
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout

data$typeName <- ifelse(data$type == 0, "3 ~", ifelse(data$type == 1, "2~", "1~"))
means$typeName <- ifelse(means$type == 0, "3 ~", ifelse(means$type == 1, "2~", "1~"))
```

styleTest4

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser, group=type, colour=typeName)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle, group=type, colour=typeName)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout, group=type, colour=typeName)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("repeatRules.csv")
data$count <- data$id * 200
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout
```

The same repeated rule, applying to 1000 elements. Graphs contain `r length(data$id)` samples.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("nonMatchingRules.csv")
data$count <- data$id * 200
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout
```

The same repeated rule with a different selector for each rule. One version applies to 1000 elements. Graphs contain `r length(data$id)` samples.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("matchingRules.csv")
data$count <- data$id * 200
means <- aggregate(data, list(data$id), FUN=mean)
stdevs <- aggregate(data, list(data$id), FUN=sd)
means$HDPpPCFBPsd <- stdevs$HTMLDocumentParser..processParsedChunkFromBackgroundParser
means$DuSsd <- stdevs$Document..updateStyle
means$FVpLsd <- stdevs$FrameView..performLayout
```

The same repeated rule with a different selector for each rule. Each rule applies to a single element. Graphs contain `r length(data$id)` samples.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(means, aes(x=count, y=HTMLDocumentParser..processParsedChunkFromBackgroundParser)) + geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser-HDPpPCFBPsd), linetype=2) +  geom_line(aes(y=HTMLDocumentParser..processParsedChunkFromBackgroundParser+HDPpPCFBPsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=Document..updateStyle)) + geom_line(aes(y=Document..updateStyle-DuSsd), linetype=2) + geom_line(aes(y=Document..updateStyle+DuSsd), linetype=2) + geom_line(size=1.1)
ggplot(means, aes(x=count, y=FrameView..performLayout)) + geom_line(aes(y=FrameView..performLayout-FVpLsd), linetype=2) +geom_line(aes(y=FrameView..performLayout+FVpLsd), linetype=2) + geom_line(size=1.1)
```